Cochain level May-Steenrod operations

### 2021-07-06 referee_reply.tex

\documentclass{article}
\usepackage{amsmath, amsfonts}
\usepackage{csquotes}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}

% sets
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}

% funtors and operators
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\End}{\mathrm{End}}

% other
\renewcommand{\th}{^{\mathrm{th}}}

\begin{document}
	\title{Referee reply for ``Chain level Steenrod operations"}
	\date{\today}
	\maketitle

	We begin by thanking the referee for their careful reading and many valuable suggestions.
	Below we include a point-by-point reply to the report.

	\section{Points raised by the referee}

	\begin{enumerate}
		\item Thank you for pointing this typo.
		We have fixed it and many other similar mistakes.
		\item We have followed all the suggestions presented in this point.
		Explicitly,
		\begin{enumerate}
			\item Change the title from ``Chain level Steenrod operations" to ``Cochain level May-Steenrod operations".
			\item Rename ``Steenrod-Adem structures" to ``May-Steenrod structures''.
			\item Add a paragraph below Definition 7 explaining in more detail the relationship between our notion of May-Steenrod structure and those considered by May in his ``A general algebraic approach to Steenrod operations''.
		\end{enumerate}
		\item
		\begin{enumerate}
			\item We greatly expanded the discussion of Adem and Cartan relations, making explicit their dependence on the proofs by May.
			We have also separated their treatment.
			The Adem relations are a consequence of the fact that a May-Steenrod structure demands a factorization with the second factor a morphism of operads.
			The (internal) Cartan relations require some compatibility with the coalgebra structure on the minimal resolution $\mathcal W$.
			Something that was missing in the previous version of this paper and that we have now corrected by introducing the notion of a ``comultiplicative May-Steenrod structure''.
			\item Add Remark 17 explaining that our map $\mathcal W \to \mathcal E$ factors through the (unreduced) bar resolution of $\mathrm C$, with the second map in the factorization induced from the chosen inclusions $\iota \colon \mathrm C_r \to \mathrm S_r$.
		\end{enumerate}
	\end{enumerate}

	\section{Other changes}
	\begin{enumerate}
		\item We have removed the appendix containing two proofs and a sketch of a third one.
		Specifically, we have moved the proof of Theorem 15 and 24 from the appendix to right below their statement, and replaced the sketch of proof of Proposition 28 with a reference to a complete proof.
		\item To motivate the consideration of the cubical viewpoint, we have included a paragraph in the introduction mentioning Baues' cubical reformulation of Adams' cobar construction.
		This implies that the constructions of this paper provides explicit descriptions of Steenrod operations on the cobar construction of chains of (reduced) simplicial sets
	\end{enumerate}
\end{document}

### 2021-07-06 effective.tex
Version sent to the referee

In this section we construct explicit May-Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ \cite{medina2020prop1}. We also define natural and effective May-Steenrod structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.

@@

\begin{figure}
	\begin{tikzcd}
	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle"'] \arrow[dddrr, bend left=20, "\phi^\square"'] & & \\
	& & \mathcal X \arrow[ru, "SL"] & & & \\
	& \mathcal E \arrow[ur, "TR"] & & & & \\
	\mathcal W \arrow[rrrr, "\psi^\triangle", bend right=10] \arrow[rrrrr, "\psi^\square", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet(X)} & \End_{N^\bullet(X)}
	\end{tikzcd}
	\caption{Summary of effective constructions: May-Steenrod structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May-Steenrod structures on the normalized chains of simplicial and cubical sets. We are abusing notation since the maps $TR$ and $SL$ required different sign conventions.}
	\label{fig: bigsummary}
\end{figure}

@@

\begin{definition} \label{def: Steenrod-Adem on Barratt-Eccles}
	For every $r \geq 0$, let $\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
	\begin{equation*}
	\psi_{\mathcal E}(r)(e_{n}) = \begin{cases}
	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \rho^{r_2}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m, \\
	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m+1,
	\end{cases}
	\end{equation*}
	where the sum is over all $r_1, \dots, r_m \in \{0, \dots, r-1\}$.
\end{definition}

@@

\begin{proof}
	This theorem follows from a computation which we defer to the appendix.
\end{proof}

@@

\begin{remark}
	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota : \mathrm C_r \to \mathrm S_r$ induces a simplicial map $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ which extends to a quasi-isomorphism of $\mathrm C$-modules
	\begin{equation*}
	N_\bullet E(\iota) : N_\bullet E(\mathrm C) \to N_\bullet E(\mathrm S) = \mathcal E,
	\end{equation*}
	factoring
	\begin{equation*}
	\psi_{\mathcal E} :
	\begin{tikzcd}
	\mathcal W \arrow[r, "\phi_{\mathrm C}"] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
	\end{tikzcd}
	\end{equation*}
\end{remark}

@@

Let us start by recalling the definition of the surjection operad. For a non-negative integer $r$ let $\mathcal X(r)_n$ be the free abelian group generated by all functions from $\{1, \dots, n+r\}$ to $\{1, \dots, r\}$ modulo the subgroup generated by degenerate functions, i.e., those which are either non-surjective or have a pair of equal consecutive values. We only describe the McClure-Smith convention since we refer to it in subsequent sections. The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s : \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
\begin{equation} \label{eq: surjection boundary}
\bigotimes_{i = 1}^r N_\bullet \big( \triangle^{s^{-1}(i)}; \Z \big).
\end{equation}
Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at the time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on. Since we do not use the composition structure we refer to \cite{mcclure03cochain} for it.

Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}. Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i : \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p : \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s : \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
with a 1, then the new sequence is degenerate so $s$ takes it to $0$. These maps satisfy
\begin{equation*}
p  i = \mathrm{id}
\qquad \text{ and } \qquad
\mathrm{id} - i  p = \partial s + s \partial.
\end{equation*}
These maps define a contraction of $\mathcal X(r)$ onto $\mathcal X(1) \cong \Z$ with homotopy $h = s + i\, s\, p + \cdots + i^{r-1} s\, p^{r-1}$, satisfying
\begin{equation*}
\partial h + h \partial = \mathrm{id} - i^{r-1}\,p^{r-1}.
\end{equation*}

\begin{definition} \label{def: Steenrod-Adem on surjection}
	For every $r \geq 0$, let $\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
	\begin{align*}
	\psi_{\mathcal X}(r)(e_0) & = (1, \dots, r), \\
	\psi_{\mathcal X}(r)(e_{2m+1}) & = h\,T\,\psi_{\mathcal X}(r)(e_{2m}), \\
	\psi_{\mathcal X}(r)(e_{2m}) & = h\,N\,\psi_{\mathcal X}(r)(e_{2m-1}),
	\end{align*}
	where $T$ and $N$ are defined in \eqref{eq: T and R definition}.
\end{definition}

@@

\begin{proof}
	This theorem follows from a computation which we defer to the appendix.
\end{proof}

@@

\subsection{The finitely presented $E_\infty$-prop $\mathcal M$}

We start by reviewing the finitely presented $E_\infty$-prop introduced in \cite{medina2020prop1}. Let $\mathcal M$ be the prop generated by 
\begin{equation*}
\counit \in \mathcal M(1,0)_0, \hspace*{.6cm} \coproduct \in \mathcal M(1,2)_0, \hspace*{.6cm} \product \in \mathcal M(2,1)_1,
\end{equation*}
with boundary
\begin{equation*}
\partial\ \counit = 0, \hspace*{.6cm} \partial \ \coproduct = 0, \hspace*{.6cm} \partial \ \product = \ \boundary \, ,
\end{equation*}
and restricted by the relations
\begin{equation*}
\productcounit, \hspace*{.6cm} \leftcounitality \, , \hspace*{.6cm} \rightcounitality \, .
\end{equation*}

Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$-prop in the terminology of Bordmann-Vogt \cite{boardman1973homotopy}. More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$-operad. For the remainder of this article we write $U(\mathcal M)$ instead of $U_2(\mathcal M)$.

We will define a May-Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May-Steenrod structure $\psi_{\mathcal X} : \mathcal W \to \mathcal X$ with a morphism of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact)
\begin{equation*}
SL \colon \mathcal X \to U(\mathcal M)
\end{equation*}
that we now define. Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element
\begin{center}
	\begin{tikzpicture}[scale=.85]
	\draw (0,0)--(0,-.6) node[below]{$\scriptstyle 1$};
	\draw (0,0)--(.5,.5);
	\draw (-.3, .3)-- (-.2,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_1$};
	\draw (-.5,.5)--(0,0);
	\node at (.11,.4){$...$};

@@

\begin{theorem} \label{thm: simplicial chain bialgebra}
	For every $n \in \mathbb{N}$, the assignment
	\begin{equation*}
	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
	\end{equation*}
	defines a natural $\mathcal M$-bialgebra structure  on $N_\bullet(\triangle^n)$.
\end{theorem}

\begin{proof}
	This statement is proven as Theorem 4.2 in \cite{medina2020prop1}.
\end{proof}

\begin{definition}
	Let $X$ be a simplicial set. Denote by $\phi^\triangle : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem \ref{thm: simplicial chain bialgebra}.
\end{definition}

@@

\begin{remark}
	The $E_\infty$-structure we described in Theorem \ref{thm: simplicial chain bialgebra}, depending solely on three fundamental maps, recovers the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and, up to signs, that of Berger-Fresse \cite{berger04combinatorial}.
\end{remark}

@@

>>>>

In this section we construct explicit May-Steenrod structures on three well know combinatorial $E_\infty$ operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$ prop $\mathcal M$ introduced in \cite{medina2020prop1}.
We also define natural and effective May-Steenrod structure on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.

@@

\begin{figure}
	\begin{tikzcd}
	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle"'] \arrow[dddrr, bend left=20, "\phi^\square"'] & & \\
	& & \mathcal X \arrow[ru, "SL"] & & & \\
	& \mathcal E \arrow[ur, "TR"] & & & & \\
	\mathcal W \arrow[rrrr, "\psi^\triangle", bend right=10] \arrow[rrrrr, "\psi^\square", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet(X)} & \End_{N^\bullet(X)}
	\end{tikzcd}
	\caption{Summary of effective constructions: May-Steenrod structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May-Steenrod structures on the normalized chains of simplicial and cubical sets. We remark that the maps $TR$ and $SL$ required different sign conventions.}
	\label{fig: bigsummary}
\end{figure}

@@

\begin{definition} \label{def: Steenrod-Adem on Barratt-Eccles}
	For every $r \geq 0$, let $\psi_{\mathcal E}(r) \colon \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
	\begin{equation*}
	\psi_{\mathcal E}(r)(e_{n}) = \begin{cases}
	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \rho^{r_2}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m, \\
	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m+1,
	\end{cases}
	\end{equation*}
	where the sum is over all $r_1, \dots, r_m \in \{0, \dots, r-1\}$.
\end{definition}

@@

\begin{proof}
	Since $\mathcal X$ is an $E_\infty$ operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
	\begin{equation*}
	\psi_{\mathcal E}(r) \colon \mathcal W(r) \to \mathcal E(r)
	\end{equation*}
	is a chain map for every $r \geq 0$.
	We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$. To show $\psi$ is a chain map we proceed by induction.
	Notice that
	\begin{equation*}
	\psi(\partial e_0) = 0 = \partial \psi(e_0)
	\end{equation*}
	and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$. If $k = 2n$ we have
	\begin{align*}
	\partial \psi(e_{2n}) & = 
	\partial \sum_{r_1, \dots, r_n} 
	\big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
	\partial \sum_{r_2, \dots, r_n} \sum_{r_1 = 0}^{p-1}
	\big(\rho^0, \rho^{r_1} \, (\rho^0, \rho^{1}, \dots, \rho^{r_n-r_1}, \rho^{r_n - r_1 +1}) \big) \\ & =
	\partial \sum_{r_2, \dots, r_n}
	\big(\rho^0, N\, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1}) \big) \\ & =
	\sum_{r_2, \dots, r_n}
	N\, \big( \rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1} \big) \\ & -
	\sum_{r_2, \dots, r_n}
	\big(\rho^0, \partial \, N \, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n+1}) \big) \\ & =
	N \psi(e_{2n-1}) - (\rho^0, \partial N \psi (e_{2n-1})) \\ & =
	\psi(N e_{2n-1}) - (\rho^0, \psi (\partial N e_{2n-1})) \\ & =
	\psi(\partial e_{2n}) - (\rho^0, \psi (\partial^2 e_{2n})) \\ & =
	\psi(\partial e_{2n}).
	\end{align*}
	If $k = 2n+1$ we have
	\begin{align*}
	\partial \psi(e_{2n+1}) & = 
	\partial \sum_{r_1, \dots, r_n} 
	\big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
	\partial \sum_{r_1, \dots, r_n}
	\big(\rho^0, \rho^{1} \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
	\partial \sum_{r_1, \dots, r_n}
	\big(\rho^0, T\, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
	\sum_{r_1, \dots, r_n}
	T \, \big( \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n} \big) \\ & -
	\sum_{r_1, \dots, r_n}
	\big(\rho^0, \partial \, T \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
	T \psi(e_{2n}) - (\rho^0, \partial T \psi (e_{2n})) \\ & =
	\psi(T e_{2n}) - (\rho^0, \psi (\partial T e_{2n})) \\ & =
	\psi(\partial e_{2n+1}) - (\rho^0, \psi (\partial^2 e_{2n+1})) \\ & =
	\psi(\partial e_{2n+1})
	\end{align*}
	where for the third equality we used that for any $r_1, \dots, r_n$
	\begin{equation*}
	(\rho^0, \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) = 0.
	\end{equation*}
	This map is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0)$ represents a generator of the homology.
\end{proof}

@@

\begin{remark}
	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota \colon \mathrm C_r \to \mathrm S_r$ induces both; a simplicial inclusion $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ and one of $\mathrm C$-modules
	\begin{equation*}
	N_\bullet E(\iota) \colon N_\bullet E(\mathrm C) \to N_\bullet E(\mathrm S) = \mathcal E.
	\end{equation*}
	We remark that the image of our map $\psi_{\mathcal E}$ lies in the subcomplex $N_\bullet E(\mathrm C)$, so the map $\psi_{\mathcal E}$ factors as
	\begin{equation*}
	\psi_{\mathcal E} \colon
	\begin{tikzcd}
	\mathcal W \arrow[r] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
	\end{tikzcd}
	\end{equation*}
\end{remark}

@@

Let us start by recalling the definition of the surjection operad.
For a non-negative integer $r$ let $\mathcal X(r)_n$ be the free abelian group generated by all functions from $\{1, \dots, n+r\}$ to $\{1, \dots, r\}$ modulo the subgroup generated by degenerate functions, i.e., those which are either non-surjective or have a pair of equal consecutive values.
We only describe the McClure-Smith convention since we refer to it in subsequent sections.
The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
\begin{equation} \label{eq: surjection boundary}
\bigotimes_{i = 1}^r N_\bullet \big( \triangle^{s^{-1}(i)}; \Z \big).
\end{equation}
Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at the time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
Since we do not use the composition structure we refer to \cite{mcclure03cochain} for it.

Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$ operad and whose introduction is credited to Benson \cite{benson1998rep}.
Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i \colon \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p \colon \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurrence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s \colon \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
with a 1, then the new sequence is degenerate so $s$ takes it to $0$.
These maps satisfy
\begin{equation*}
p i = \mathrm{id}
\qquad \text{ and } \qquad
\mathrm{id} - i  p = \partial s + s \partial.
\end{equation*}
The compositions $i^{r-1}$ and $s^{r-1}$ define a contraction of $\mathcal X(r)$ onto $\mathcal X(1) \cong \Z$ with homotopy
\begin{equation*}
h = s + i\, s\, p + \cdots + i^{r-1} s\, p^{r-1},
\end{equation*}
i.e., they satisfy
\begin{equation*}
p^{r-1} i^{r-1} = \mathrm{id}
\qquad \text{ and } \qquad
\partial h + h \partial = \mathrm{id} - i^{r-1}\,p^{r-1}.
\end{equation*}

\begin{definition} \label{def: Steenrod-Adem on surjection}
	For every $r \geq 0$, let $\psi_{\mathcal X}(r) \colon \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
	\begin{align*}
	\psi_{\mathcal X}(r)(e_0) & = (1, \dots, r), \\
	\psi_{\mathcal X}(r)(e_{2m+1}) & = h\,T\,\psi_{\mathcal X}(r)(e_{2m}), \\
	\psi_{\mathcal X}(r)(e_{2m}) & = h\,N\,\psi_{\mathcal X}(r)(e_{2m-1}),
	\end{align*}
	where $T$ and $N$ are defined in \eqref{eq: T and R definition}.
\end{definition}

@@

\begin{proof}
	Since $\mathcal X$ is an $E_\infty$ operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
	\begin{equation*}
	\psi_{\mathcal X}(r) \colon \mathcal W(r) \to \mathcal X(r)
	\end{equation*}
	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a chain map for every $r \geq 0$. We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$. To show $\psi$ is a chain map we proceed by induction. Notice that
	\begin{equation*}
	\psi(\partial e_0) = 0 = \partial \psi(e_0)
	\end{equation*}
	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$. For $n = 2m+1$ we have
	\begin{align*}
	\partial \psi(e_{2m+1}) 
	& =
	\partial\, h\, T\, \psi(e_{2m}) \big) \\
	& =
	T\, \psi(e_{2m}) - i^{r-1} p^{r-1}\, \psi(e_{2m}) -
	h\, \partial\, T\, \psi(e_{2m}) \big) \\
	& =
	T\, \psi(e_{2m}) - 
	h\, T\, \psi(\partial\, e_{2m}) \big) \\
	& =
	T\, \psi(e_{2m}) - 
	h\, \psi(T\,N\, e_{2m-1}) \big) \\
	& = 
	T \psi(e_{2m}).
	\end{align*}
	For $n = 2m$ the proof is analogous. The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
\end{proof}

@@

\subsection{The $E_\infty$ prop $\mathcal M$}

We start by reviewing the finitely presented $E_\infty$ prop introduced in \cite{medina2020prop1}.
Let $\mathcal M$ be the prop generated by 
\begin{equation*}
\counit \in \mathcal M(1,0)_0, \hspace*{.6cm} \coproduct \in \mathcal M(1,2)_0, \hspace*{.6cm} \product \in \mathcal M(2,1)_1,
\end{equation*}
with boundary
\begin{equation*}
\partial\ \counit = 0, \hspace*{.6cm} \partial \ \coproduct = 0, \hspace*{.6cm} \partial \ \product = \ \boundary \, ,
\end{equation*}
and restricted by the relations
\begin{equation*}
\productcounit, \hspace*{.6cm} \leftcounitality \, , \hspace*{.6cm} \rightcounitality \, .
\end{equation*}

Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$ prop as introduced in Definition~\ref{def: e-infinity operad and prop}.
More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$ operad.
For the remainder of this article we write $U(\mathcal M)$ instead of $U_2(\mathcal M)$.

We will define a May-Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May-Steenrod structure $\psi_{\mathcal X} \colon \mathcal W \to \mathcal X$ with a morphism $SL \colon \mathcal X \to U(\mathcal M)$ of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact) that we now define.
Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element represented by the connected $(1,r)$-graph
\begin{center}
	\begin{tikzpicture}[scale=.85]
	\draw (0,0)--(0,-.6) node[below]{$\scriptstyle 1$};
	\draw (0,0)--(.5,.5);
	\draw (-.3, .3)-- (-.2,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_1$};
	\draw (-.5,.5)--(0,0);
	\node at (.11,.4){$...$};

@@

\begin{proposition}[\cite{medina2020prop1}] \label{prop: simplicial chain bialgebra}
	For every $n \in \mathbb{N}$, the assignment
	\begin{equation*}
	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
	\end{equation*}
	defines a natural $\mathcal M$-bialgebra structure  on $N_\bullet(\triangle^n)$, and, through a Kan extension argument, a natural $U(\mathcal M)$-algebra structure $\phi^\triangle \colon U(\mathcal M) \to \End_{N^\bullet (X)}$ on the cochains of any simplicial set $X$.
\end{proposition}

Composing the algebra structure $\phi^\triangle$ with the May-Steenrod structure on $U(\mathcal M)$ gives a natural May-Steenrod structure on $N^\bullet(X)$.
We record this observation in the following.

@@

\begin{remark}
	The $E_\infty$ structure we described in Proposition~\ref{prop: simplicial chain bialgebra}, depending solely on three fundamental maps, generalizes the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}, please consult \cite{medina2020prop1} for more details.
\end{remark}

We will now give examples of how this May-Steenrod structure defines representatives of Steenrod operations for simplicial cochains.
For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$ for Steenrod operations.

@@

We will now give examples of how this May-Steenrod structure defines representatives of Steenrod operations for cubical cochains.
Recall the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$ for Steenrod operations used when studying the cohomology of spaces.
